### 2016-09-05 Paper/mnras_template.tex
Little paragraph about Illustris

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[K. T. Smith et al.]{
Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a high resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content. This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$ together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ in a periodic box of $106.5\text{Mpc}$, which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0.809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
^{-1}\text{Mpc}^{-1}$. Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution for DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation. The evolution for the particles   \\

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2016-09-06 Paper/mnras_template.tex
dsada

@@
 \section{Illustris Simulation}
-Illustris-1, also known simply as Illustris, is a high resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.
-This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$ together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ in a periodic box of $106.5\text{Mpc}$, which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0.809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
+Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.
+This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0.809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
 ^{-1}\text{Mpc}^{-1}$.
-Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution for DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation.
-The evolution for the particles   \\
+Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation.
+The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines an moving Voronoi tessellation with the finite volume approach.
+Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs.
+The level of detail in Illustris is advantageous and hard to find among other simulations, and is the reason why we chose it to perform our calculations.\\
+
+This simulation consists of 136 snapshots where 61 of them were taken at $z < 3$ spaced with a cosmological scale factor $\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$ with spacing $\Delta a \approx 0.01$.
+Each snapshot was post-processed with modified versions of FOF and SUBFIND algorithms \cite{fof,subfind} to generate halo and subhalo catalogues with their respective characterization properties.
 

### 2017-04-11 Paper/mnras_template.tex
Wrote sth

@@
 Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation.
-The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines an moving Voronoi tessellation with the finite volume approach.
+The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach.
 Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs.
@@
 
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
+\section{The method}
+The principal purpose of this work is to verify if the results obtained observationally by Jones et al.
+\cite{jones1} are supported by a similar analysis in the cosmological simulation Illustris.
+For this purpose, we want to adaptate the observational method as closely as posible for it to work on computational data.\\
 
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
+The principal method used in Jones et al.
+\cite{jones1} for the analysis of the dependence of the Schechter parameters on the cosmological environment is as follows.
+To obtain a quantification of environment, they calculated for, each galaxy in the studied survey, the projected distance in the sky to the third nearest neighbor, filtrating candidate galaxies by its radial velocity relative to the galaxy studied.
+According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the projection method.
+The radial relative velocity cut was chosen to be $450km/s$.
+Furthermore, a photometrics preselection was performed, selecting galaxies whose r-filter magnitude was above $-19$ (VERIFY).\\
 
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
+Once quantified the environment with the distance to the 3rd nearest neighbor definition for each galaxy in their post-selected survey they divided the group in four quartiles according this quantity.
+For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained.
+The analysis was specifically performed over the Schechter parameters of the Knee-mass and the faint-end slope.\\
 
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
+In dark matter cosmological simulations, acces to the information is istantaneous and at no cost.
+However, as we want to replicate as closely as possible the method effectuated by Jones et.
+al \cite{jones1}.
+We also calculate the projected distance in the simulation, according to a specified point of view, taking the same radial velocity cut having into account distance and peculiar velocities.
+Even when we could easily calculate the distance to the third nearest neighbor we take into account these observational simplifications, to make our study as comparable as possible to that of Jones et al.
+\cite{jones1}
 
-\subsection{Figures and tables}
+\section{Results}
+\subsection{Preliminaries}
+
+\subsection{Mass functions comparison}
 
@@
 
-% Example figure
+% Quartiles gas
 \begin{figure}
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
+	\includegraphics[width=\columnwidth]{./pics/quartilesGas.png}
+    \caption{\textbf{Upper side}: Schechter fits of each gas mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:quartilesGas}
+\end{figure}
+
+% Tweb gas
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/T-Web_Gas.png}
+    \caption{\textbf{Upper side}: Schechter fits of each gas mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:TwebGas}
+\end{figure}
+
+% Quartiles DM
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/quartilesDM.png}
+    \caption{\textbf{Upper side}: Schechter fits of each DM mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:quartilesDM}
+\end{figure}
+
+% Tweb DM
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/T-Web_DM.png}
+    \caption{\textbf{Upper side}: Schechter fits of each DM mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:TwebDM}
+\end{figure}
+
+% Quartiles Stellar
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/quartilesSellar.png}
+    \caption{\textbf{Upper side}: Schechter fits of each stellar mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:quartilesStellar}
+\end{figure}
+
+% Tweb Stellar
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/T-Web_Stellar.png}
+    \caption{\textbf{Upper side}: Schechter fits of each stellar mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:TwebStellar}
+\end{figure}
+
+% Quartiles BH
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/quartilesBH.png}
+    \caption{\textbf{Upper side}: Schechter fits of each BH mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:quartilesBH}
+\end{figure}
+
+% Tweb BH
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/T-Web_BH.png}
+    \caption{\textbf{Upper side}: Schechter fits of each BH mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \label{fig:TwebBH}
 \end{figure}

### 2017-06-06 Paper/mnras_template.tex
Some advances

@@
 Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.
-This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0.809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
+This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
 ^{-1}\text{Mpc}^{-1}$.
 Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation.
+\\
+
 The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach.
@@
 \section{The method}
+
 The principal purpose of this work is to verify if the results obtained observationally by Jones et al.
@@
 
+\subsection{The $3^{rd}$ nearest neighbor method}
+
 The principal method used in Jones et al.
-\cite{jones1} for the analysis of the dependence of the Schechter parameters on the cosmological environment is as follows.
-To obtain a quantification of environment, they calculated for, each galaxy in the studied survey, the projected distance in the sky to the third nearest neighbor, filtrating candidate galaxies by its radial velocity relative to the galaxy studied.
+\cite{jones1} analyses the dependence of the Schechter parameters on the cosmological environment.
+To obtain a quantification of said cosmological environment, they calculated for each galaxy in the studied survey the projected distance in the sky to the third nearest neighbor, filtrating candidate neighbors by its radial velocity relative to the reference galaxy.
 According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the projection method.
 The radial relative velocity cut was chosen to be $450km/s$.
-Furthermore, a photometrics preselection was performed, selecting galaxies whose r-filter magnitude was above $-19$ (VERIFY).\\
+Furthermore, a photometrics pre-selection was performed, selecting galaxies whose r-filter magnitude was above $-19$ (VERIFY).\\
 
@@
 For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained.
-The analysis was specifically performed over the Schechter parameters of the Knee-mass and the faint-end slope.\\
+The analysis was specifically performed over the Schechter parameters of the Knee-mass and the faint-end slope.
+\\
 
-In dark matter cosmological simulations, acces to the information is istantaneous and at no cost.
+In dark matter cosmological simulations, access to the information is istantaneous and at no cost.
 However, as we want to replicate as closely as possible the method effectuated by Jones et.
-al \cite{jones1}.
-We also calculate the projected distance in the simulation, according to a specified point of view, taking the same radial velocity cut having into account distance and peculiar velocities.
+al \cite{jones1}, we also calculate the projected distance in the simulation and take the same projected velocity cut according to a specified point of view.
 Even when we could easily calculate the distance to the third nearest neighbor we take into account these observational simplifications, to make our study as comparable as possible to that of Jones et al.
-\cite{jones1}
+\cite{jones1}.\\
+
+However, as Illustris is a cosmological simulation, it is subject to numerical resolution biases, being the most important, the mass resolution biases.
+Each mass considered here is subject directly or indirectly to a mass resolution, and the effect it causes is specially evident in the produced mass functions.
+We used Illustris-3, which is a less resoluted copy of Illustris-1, to verify that the effect on the mass functions is indeed caused by mass resolution.
+Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
+This mass cut has no aparent systematical way to be calculated and therefore, we performed the cut having into account the performance of the respective Schechter fit.\\
+
+Mass resolution reduces the size of the sample galaxies and this complicates the process of photometrics pre-selection.
+This selection significatively reduces the size of the galaxy set which is already smaller than normal due to the resolution cut.
+This made impossible a Schechter fit to the obtained mass functions given that the associated logarithmic errors became extremely large.
+For this reason, we omit the photometrics pre-selection which is the only feature that our analysis misses with respect to the one from \cite{jones1}.\\
+
+\subsection{The cosmic web method}
+To complement the analysis performed with the third nearest neighbor method for the classification of environments, we chose a complementary method of completely different nature to verify even more the results from Jones et al..
+The method chosen here was
 

### 2017-08-18 Paper/mnras_template.tex
Some advances
Small improvement of illustris section

@@
 \section{Illustris Simulation}
-Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.
-This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
-^{-1}\text{Mpc}^{-1}$.
+Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.\\
+
+This was achieved by following the evolution of $2 \times 1820^3$ elements with dark mass resolution of $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$ and initial baryonic mass resolution of $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration in a periodic box of $106.5\text{Mpc}$.
+The $\Lambda \text{CDM}$ cosmology of this run follows: $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
+^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy Probe (WMAP)-9 \cite{AnisotropyProbe}.
 Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation.
@@
 
-The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach.
+The evolution in time was performed with the hydrodynamic code AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach.
 Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs.
-The level of detail in Illustris is advantageous and hard to find among other simulations, and is the reason why we chose it to perform our calculations.\\
+Specifically, the physics followed by this model includes energetic feedback from supermassive black holes and supernovae, as well as stellar evolution and chemical enrichment.
+This level of detail in Illustris is advantageous for the analysis of the effect of the environment  in galactic barionic properties and is hard to find among other simulations, i.e.
+post-processed runs with semi-analytical models which do not directly simulate baryons.(Expand) Describe Arepo a little bit more\\
 
-This simulation consists of 136 snapshots where 61 of them were taken at $z < 3$ spaced with a cosmological scale factor $\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$ with spacing $\Delta a \approx 0.01$.
-Each snapshot was post-processed with modified versions of FOF and SUBFIND algorithms \cite{fof,subfind} to generate halo and subhalo catalogues with their respective characterization properties.
+The output of this simultaion consists of 136 snapshots where 61 of them were taken at $z < 3$ spaced with a cosmological scale factor $\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$ with spacing $\Delta a \approx 0.01$.
+Each snapshot was post-processed with a modified version of FOF \cite{FOF} to identify DM haloes with more than 32 particles using a linking length of 0.2 times the mean particle separation each of which is analyzed with the SUBFIND algorithm \cite{subfind} to generate, at z=0, 7,713,601 halos (FOF) and 4,366,546 (sub)halo catalogues with their respective characterization properties.
+\\
+
+(HERE TALK ABOUT ILLUSTRIS-2,3 FOR RESOLUTION PURPOSES)
 
@@
 To complement the analysis performed with the third nearest neighbor method for the classification of environments, we chose a complementary method of completely different nature to verify even more the results from Jones et al..
-The method chosen here was
+The method chosen here was the one developed by Forero et al.
+\cite{forero1}, which uses the Hessian of the gravitational potential obtained from the DM field to classify galaxies into (conveniently) four morphological environments.\\
 

### 2017-08-29 Illustris_Run/Code/Illustris_Cluster.py
Phase space files for Illustris 1 2 and 3

@@ -1,0 +1,27 @@
+import numpy as np
+from arepo import *
+
+# Path of the simulations
+path1 = "/hits/universe/Illustris/L75n1820C/" 
+path2 = "/hits/universe/Illustris/L75n910FP/" 
+path3 = "/hits/universe/Illustris/L75n455FP/"
+# Filenames
+filenames = ['Illustris1','Illustris2','Illustris3']
+# Snapshot number
+snapnum = 135
+for path,filename in zip([path1,path2,path3],filenames): 
+ 
+    # Loads groups to select the principal halo
+    subSn = Subfind(path,snapnum)
+    
+    # Loads important data
+    pos  = subSn.subhalo.SubhaloPos
+    vel  = subSn.subhalo.SubhaloVel
+    mass = subSn.subhalo.SubhaloMassType
+    
+    # Creates and fills the numpy array to save
+    arr = np.zeros((len(pos),12))
+    arr[:,:3]  = pos
+    arr[:,3:6] = vel
+    arr[:,6:]  = mass
+    np.savetxt("../data/phaseSpace/"+filename+".txt",arr)

### 2017-08-29 Illustris_Run/Code/Illustris_Cluster.py
Reordering

@@ -1,27 +1,0 @@
-import numpy as np
-from arepo import *
-
-# Path of the simulations
-path1 = "/hits/universe/Illustris/L75n1820C/" 
-path2 = "/hits/universe/Illustris/L75n910FP/" 
-path3 = "/hits/universe/Illustris/L75n455FP/"
-# Filenames
-filenames = ['Illustris1','Illustris2','Illustris3']
-# Snapshot number
-snapnum = 135
-for path,filename in zip([path1,path2,path3],filenames): 
- 
-    # Loads groups to select the principal halo
-    subSn = Subfind(path,snapnum)
-    
-    # Loads important data
-    pos  = subSn.subhalo.SubhaloPos
-    vel  = subSn.subhalo.SubhaloVel
-    mass = subSn.subhalo.SubhaloMassType
-    
-    # Creates and fills the numpy array to save
-    arr = np.zeros((len(pos),12))
-    arr[:,:3]  = pos
-    arr[:,3:6] = vel
-    arr[:,6:]  = mass
-    np.savetxt("../data/phaseSpace/"+filename+".txt",arr)

### 2017-08-29 Illustris_Run/Code/Illustris_Reader.py

@@ -1,74 +1,0 @@
-import numpy as np
-import illustris_python as il
-import sys
-import time
-# Generates the basepath depending on the simulation by parameter
-basePath = "./Illustris-1"
-
-######################################################
-#                   Load Subhalos                    #
-######################################################
-start_time = time.time()
-
-# Selects the fields to load for subhalos
-fields = ['SubhaloCM','SubhaloVel','SubhaloStellarPhotometrics','SubhaloMassType']
-# Loads subhalos in g
-g = il.groupcat.loadSubhalos(basePath,135,fields=fields)
-
-# Filters galaxies by magnitude
-print "Filtering galaxies by magnitude..."
-print "Number of galaxies before: " + str(g['count'])
-# Creates lists for galaxies that fulfill the condition
-gr = []
-gv = []
-# Filter the galaxies for its photometrics (only rband < -19)
-i = 0
-for i in range(g['count']):
-    if g['SubhaloStellarPhotometrics'][i][5] > -19.0:
-        gr.append([g['SubhaloCM'][i][0],g['SubhaloCM'][i][1],g['SubhaloCM'][i][2]])
-        gv.append([g['SubhaloVel'][i][0],g['SubhaloVel'][i][1],g['SubhaloVel'][i][2]])
-
-gr = np.array(gr)
-gv = np.array(gv)
-g['count'] = len(gr)
-
-print "Number of galaxies after: " + str(len(gr))
-print "Time elapsed: " + str(time.time() - start_time)
-
-
-
-######################################################
-#                     Load Halos                     #
-######################################################
-
-# Selects the fields to load for haloes
-fields = ['GroupPos','GroupVel','GroupFirstSub','GroupMassType']
-h = il.groupcat.loadHalos(basePath,135,fields=fields)
-#print "LOL ya.\n"
-
-# Creates the arrays to convert to files
-print "Formating info..."
-Halos = np.array([[0,0,0,0,0,0] for i in range(h['count']) ])
-Galaxies = np.array([[0,0,0,0,0,0] for i in range(g['count']) ])
-
-# Fills the arrays
-for i in range(h['count']):
-    Halos[i][0] = h['GroupPos'][i][0]
-    Halos[i][1] = h['GroupPos'][i][1]
-    Halos[i][2] = h['GroupPos'][i][2]
[…]

### 2017-08-29 Illustris_Run/Code/environment.c

@@ -1,489 +1,0 @@
-/*
- * This program calculates the environment for each halo in Halo.csv
- * The environment is defined as the area projected for nth nearest galaxy
- * conditions for neighbouring galaxies:
- *          -rmag < -19 (already filtered in Galaxy.csv)
- *          -radial velocity relative to the halo < 500km/s
- */
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <math.h>
-#include <time.h>
-
-//------------------------------------------------------------------------------
-//   Definitions
-//------------------------------------------------------------------------------
-
-// env.csv : the name of the file to write the environments
-#define man "./environment.x Galaxyn.csv env.data"
-// Define the name for the halo and galaxy files
-//define Gdata "Galaxy3.csv"
-// Simulation constants
-#define Hubb 100.0*0.001      // Hubble constant (km/kpc)
-#define lh 0.7           // Little h (confirm)
-#define L 106500.0          // The size of the box in the simulation in kpc
-#define L_h 75000.0         // L/lh
-// Method parameters
-#define nn 3             // Nearest neighbor for environment definition
-#define ddd 0           // Defines the range in the grid to count neighbor candidates
-#define res 3.0       // The resolution of the 3d spatial grid
-
-
-//------------------------------------------------------------------------------
-//  Structs
-//------------------------------------------------------------------------------
-
-/*
- * Chain list
- */
-struct List{
-  // El hijo proximo
-  struct List* next;
-  // El ultimo hijo
-  struct List* last;
-  // El indice que guarda el tetraedro correspondiente
-  //(Permite sacar las matrices, los vecref y los volumenes)
-  int index;
-  // Guarda la longitud de la lista (solo la guarda el primero, o ahi vemos)
-  //unsigned int n;
-};
-typedef struct List List;
-
-
-//------------------------------------------------------------------------------
-//   Methods declaration
[…]

### 2017-08-29 Illustris_Run/Code/modulus.c

@@ -1,55 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <time.h>
-
-
-#define x_size 10
-float deltaPBC1(float x, float y);
-float deltaPBC2(float x, float y);
-
-int main(int argc, char **argv){
-  /*
-  int i;
-  float x = atof(argv[1]);
-  float y = atof(argv[2]);
-  printf("dx = %f, %f \n", deltaPBC1(x,y), deltaPBC2(x,y));
-  */
-  FILE* data = fopen( "data.data", "r" );
-  int test,count;
-  float x;
-  count = 0;
-  int c = 0;
-  do{
-
-    test = fscanf(data, "%f\n", &x);
-    if( x != 0){
-      //printf("________%f\n",sqrt(x));
-      count++;
-    }
-    if( x == 9e+12){
-      c++;
-    }
-    //printf("%d_%d_%d_\n",(int)floorf(x/(L/res)),(int)floorf(y/(L/res)),(int)floorf(z/(L/res)));
-
-  }while( test!=EOF );
-  printf("FIN__%d__%d\n",count, c);
-  return 0;
-}
-
-float deltaPBC1(float x, float y){
-  float dx = x - y;
-  if(dx >   x_size * 0.5){
-    dx = dx - x_size;
-  }
-  else if (dx <= -x_size * 0.5){
-    dx = dx + x_size;
-  }
-  return dx;
-}
-
-float deltaPBC2(float x, float y){
-  float dx = x - y;
-  dx = dx - truncf(dx / x_size) * x_size;
-  return dx;
-}

### 2017-08-29 Illustris_Run/Code/read_tweb.py

@@ -1,124 +1,0 @@
-import struct
-import numpy as np
-import matplotlib.pyplot as plt
-import illustris_python as il
-import time
-
-def read_CIC_scalar(filename):
-    f = open(filename, "rb")
-    dumb = f.read(38)
-
-    dumb = f.read(4)
-    n_x = f.read(4)
-    n_y = f.read(4)
-    n_z = f.read(4)
-    nodes = f.read(8)
-    x0 = f.read(4)
-    y0 = f.read(4)
-    z0 = f.read(4)
-    dx = f.read(4)
-    dy = f.read(4)
-    dz = f.read(4)
-    dumb = f.read(4)
-
-    n_x = (struct.unpack('i', n_x))[0]
-    n_y = (struct.unpack('i', n_y))[0]
-    n_z = (struct.unpack('i', n_z))[0]
-    nodes = (struct.unpack('q', nodes))[0]
-    dx = (struct.unpack('f', dx))[0]
-    dy = (struct.unpack('f', dy))[0]
-    dz = (struct.unpack('f', dz))[0]
-    x0 = (struct.unpack('f', x0))[0]
-    y0 = (struct.unpack('f', y0))[0]
-    z0 = (struct.unpack('f', z0))[0]
-    print n_x, n_y, n_z, nodes, dx, dy, dz
-
-    total_nodes = n_x * n_y *n_z
-    dumb = f.read(4)
-    array_data = f.read(total_nodes*4)
-    dumb = f.read(4)
-    format_s = str(total_nodes)+'f'
-    array_data = struct.unpack(format_s, array_data)
-    f.close()
-    array_data  = np.array(array_data)
-    array_data.resize(n_z,n_y,n_x)
-    array_data = array_data.transpose()
-    return {'eigenval':array_data, 'delta_x':dx}
-
-data = read_CIC_scalar("../data/tweb/snap_135.s1.00.eigen_1")
-eigen1 = data['eigenval']
-data = read_CIC_scalar("../data/tweb/snap_135.s1.00.eigen_2")
-eigen2 = data['eigenval']
-data = read_CIC_scalar("../data/tweb/snap_135.s1.00.eigen_3")
-eigen3 = data['eigenval']
-#print("delta_x", data['delta_x'])
-#print("shape", np.shape(data['eigenval']))
-
-
-# Size of grid cells
-delx = data['delta_x']
-
-######################################################
-#             Environment from eigen vals            #
-######################################################
-def getEnv(x,y,z):
[…]

### 2017-08-29 Illustris_Run/Code/C_libs/environment.c
Reordering

@@ -1,0 +1,489 @@
+/*
+ * This program calculates the environment for each halo in Halo.csv
+ * The environment is defined as the area projected for nth nearest galaxy
+ * conditions for neighbouring galaxies:
+ *          -rmag < -19 (already filtered in Galaxy.csv)
+ *          -radial velocity relative to the halo < 500km/s
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <math.h>
+#include <time.h>
+
+//------------------------------------------------------------------------------
+//   Definitions
+//------------------------------------------------------------------------------
+
+// env.csv : the name of the file to write the environments
+#define man "./environment.x Galaxyn.csv env.data"
+// Define the name for the halo and galaxy files
+//define Gdata "Galaxy3.csv"
+// Simulation constants
+#define Hubb 100.0*0.001      // Hubble constant (km/kpc)
+#define lh 0.7           // Little h (confirm)
+#define L 106500.0          // The size of the box in the simulation in kpc
+#define L_h 75000.0         // L/lh
+// Method parameters
+#define nn 3             // Nearest neighbor for environment definition
+#define ddd 0           // Defines the range in the grid to count neighbor candidates
+#define res 3.0       // The resolution of the 3d spatial grid
+
+
+//------------------------------------------------------------------------------
+//  Structs
+//------------------------------------------------------------------------------
+
+/*
+ * Chain list
+ */
+struct List{
+  // El hijo proximo
+  struct List* next;
+  // El ultimo hijo
+  struct List* last;
+  // El indice que guarda el tetraedro correspondiente
+  //(Permite sacar las matrices, los vecref y los volumenes)
+  int index;
+  // Guarda la longitud de la lista (solo la guarda el primero, o ahi vemos)
+  //unsigned int n;
+};
+typedef struct List List;
+
+
+//------------------------------------------------------------------------------
+//   Methods declaration
[…]

### 2017-08-29 Illustris_Run/Code/Py_libs/Illustris_Cluster.py

@@ -1,0 +1,33 @@
+import numpy as np
+from arepo import *
+
+# Path of the simulations
+path1 = "/hits/universe/Illustris/L75n1820C/" 
+path2 = "/hits/universe/Illustris/L75n910FP/" 
+path3 = "/hits/universe/Illustris/L75n455FP/"
+# Filenames
+filenames = ['Illustris1','Illustris2','Illustris3']
+# Snapshot number
+snapnum = 135
+for path,filename in zip([path1,path2,path3],filenames): 
+ 
+    # Loads groups to select the principal halo
+    subSn = Subfind(path,snapnum)
+    
+    # Loads important data
+    pos  = subSn.subhalo.SubhaloPos
+    vel  = subSn.subhalo.SubhaloVel
+    mass = subSn.subhalo.SubhaloMassType
+
+    # Have into account only subhalos with mass
+    ind, = np.where(mass[:,0]>0)
+    pos  = pos[ind]
+    vel  = vel[ind]
+    mass = mass[ind]
+
+    # Creates and fills the numpy array to save
+    arr = np.zeros((len(pos),12))
+    arr[:,:3]  = pos
+    arr[:,3:6] = vel
+    arr[:,6:]  = mass
+    np.savetxt("../data/phaseSpace/"+filename+".txt",arr)

### 2017-08-29 Illustris_Run/Code/Py_libs/Illustris_Reader.py

@@ -1,0 +1,74 @@
+import numpy as np
+import illustris_python as il
+import sys
+import time
+# Generates the basepath depending on the simulation by parameter
+basePath = "./Illustris-1"
+
+######################################################
+#                   Load Subhalos                    #
+######################################################
+start_time = time.time()
+
+# Selects the fields to load for subhalos
+fields = ['SubhaloCM','SubhaloVel','SubhaloStellarPhotometrics','SubhaloMassType']
+# Loads subhalos in g
+g = il.groupcat.loadSubhalos(basePath,135,fields=fields)
+
+# Filters galaxies by magnitude
+print "Filtering galaxies by magnitude..."
+print "Number of galaxies before: " + str(g['count'])
+# Creates lists for galaxies that fulfill the condition
+gr = []
+gv = []
+# Filter the galaxies for its photometrics (only rband < -19)
+i = 0
+for i in range(g['count']):
+    if g['SubhaloStellarPhotometrics'][i][5] > -19.0:
+        gr.append([g['SubhaloCM'][i][0],g['SubhaloCM'][i][1],g['SubhaloCM'][i][2]])
+        gv.append([g['SubhaloVel'][i][0],g['SubhaloVel'][i][1],g['SubhaloVel'][i][2]])
+
+gr = np.array(gr)
+gv = np.array(gv)
+g['count'] = len(gr)
+
+print "Number of galaxies after: " + str(len(gr))
+print "Time elapsed: " + str(time.time() - start_time)
+
+
+
+######################################################
+#                     Load Halos                     #
+######################################################
+
+# Selects the fields to load for haloes
+fields = ['GroupPos','GroupVel','GroupFirstSub','GroupMassType']
+h = il.groupcat.loadHalos(basePath,135,fields=fields)
+#print "LOL ya.\n"
+
+# Creates the arrays to convert to files
+print "Formating info..."
+Halos = np.array([[0,0,0,0,0,0] for i in range(h['count']) ])
+Galaxies = np.array([[0,0,0,0,0,0] for i in range(g['count']) ])
+
+# Fills the arrays
+for i in range(h['count']):
+    Halos[i][0] = h['GroupPos'][i][0]
+    Halos[i][1] = h['GroupPos'][i][1]
+    Halos[i][2] = h['GroupPos'][i][2]
[…]

### 2017-08-29 Illustris_Run/Code/Py_libs/read_tweb.py

@@ -1,0 +1,124 @@
+import struct
+import numpy as np
+import matplotlib.pyplot as plt
+import illustris_python as il
+import time
+
+def read_CIC_scalar(filename):
+    f = open(filename, "rb")
+    dumb = f.read(38)
+
+    dumb = f.read(4)
+    n_x = f.read(4)
+    n_y = f.read(4)
+    n_z = f.read(4)
+    nodes = f.read(8)
+    x0 = f.read(4)
+    y0 = f.read(4)
+    z0 = f.read(4)
+    dx = f.read(4)
+    dy = f.read(4)
+    dz = f.read(4)
+    dumb = f.read(4)
+
+    n_x = (struct.unpack('i', n_x))[0]
+    n_y = (struct.unpack('i', n_y))[0]
+    n_z = (struct.unpack('i', n_z))[0]
+    nodes = (struct.unpack('q', nodes))[0]
+    dx = (struct.unpack('f', dx))[0]
+    dy = (struct.unpack('f', dy))[0]
+    dz = (struct.unpack('f', dz))[0]
+    x0 = (struct.unpack('f', x0))[0]
+    y0 = (struct.unpack('f', y0))[0]
+    z0 = (struct.unpack('f', z0))[0]
+    print n_x, n_y, n_z, nodes, dx, dy, dz
+
+    total_nodes = n_x * n_y *n_z
+    dumb = f.read(4)
+    array_data = f.read(total_nodes*4)
+    dumb = f.read(4)
+    format_s = str(total_nodes)+'f'
+    array_data = struct.unpack(format_s, array_data)
+    f.close()
+    array_data  = np.array(array_data)
+    array_data.resize(n_z,n_y,n_x)
+    array_data = array_data.transpose()
+    return {'eigenval':array_data, 'delta_x':dx}
+
+data = read_CIC_scalar("../data/tweb/snap_135.s1.00.eigen_1")
+eigen1 = data['eigenval']
+data = read_CIC_scalar("../data/tweb/snap_135.s1.00.eigen_2")
+eigen2 = data['eigenval']
+data = read_CIC_scalar("../data/tweb/snap_135.s1.00.eigen_3")
+eigen3 = data['eigenval']
+#print("delta_x", data['delta_x'])
+#print("shape", np.shape(data['eigenval']))
+
+
+# Size of grid cells
+delx = data['delta_x']
+
+######################################################
+#             Environment from eigen vals            #
+######################################################
+def getEnv(x,y,z):
[…]

### 2017-08-31 Illustris_Run/Code/Py_libs/Illustris_Cluster.py
Parallelized environment script

@@ -1,3 +1,9 @@
+# This script reads Illustris1,2 &3 to produce files containing phaseSpace as well as the masses info of subhalos and 
+# Phase space info is kept in ..../Illustris_Run/data/phaseSpace/Illustris{1..3}.csv
+# Masses are kept in ..../Illustris_Run/data/Galaxy{1..3}.csv
+# Phase space format is:     x,y,z,vx,vy,vz,mG,mDM
+# Masses format is:    mG,mDM,m_,m_,mStellar,mBH
+
 import numpy as np
 from arepo import *
 
@@ -5,29 +11,33 @@ from arepo import *
 path1 = "/hits/universe/Illustris/L75n1820C/" 
 path2 = "/hits/universe/Illustris/L75n910FP/" 
 path3 = "/hits/universe/Illustris/L75n455FP/"
-# Filenames
+# Filenames for phaseSpace
 filenames = ['Illustris1','Illustris2','Illustris3']
+massFilenames = ['Galaxy1','Galaxy2','Galaxy3']
 # Snapshot number
 snapnum = 135
-for path,filename in zip([path1,path2,path3],filenames): 
+for path,filename,massfn in zip([path1,path2,path3],filenames,massFilenames): 
  
     # Loads groups to select the principal halo
-    subSn = Subfind(path,snapnum)
+    subSn = Subfind(path,snapnum,combineFiles=True, verbose = True)
     
     # Loads important data
-    pos  = subSn.subhalo.SubhaloPos
-    vel  = subSn.subhalo.SubhaloVel
-    mass = subSn.subhalo.SubhaloMassType
+    pos  = subSn.SubhaloPos
+    vel  = subSn.SubhaloVel
+    mass = subSn.SubhaloMassType
 
     # Have into account only subhalos with mass
-    ind, = np.where(mass[:,0]>0)
+    ind, = np.where(mass.T[0]>0)
+    print(len(pos))
     pos  = pos[ind]
     vel  = vel[ind]
     mass = mass[ind]
 
     # Creates and fills the numpy array to save
-    arr = np.zeros((len(pos),12))
+    arr = np.zeros((len(pos),8),dtype = np.float)
     arr[:,:3]  = pos
     arr[:,3:6] = vel
-    arr[:,6:]  = mass
-    np.savetxt("../data/phaseSpace/"+filename+".txt",arr)
+    arr[:,6:]  = mass[:,:2]
[…]

### 2017-08-31 Paper/paper.tex
update name

--- 2017-08-18 Paper/mnras_template.tex
@@
 % out the following line
-\usepackage{newtxtext,newtxmath}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+\cite{Tweb}.
 
@@
 
-The principal method used in Jones et al.
-\cite{jones1} analyses the dependence of the Schechter parameters on the cosmological environment.
-To obtain a quantification of said cosmological environment, they calculated for each galaxy in the studied survey the projected distance in the sky to the third nearest neighbor, filtrating candidate neighbors by its radial velocity relative to the reference galaxy.
-According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the projection method.
-The radial relative velocity cut was chosen to be $450km/s$.
-Furthermore, a photometrics pre-selection was performed, selecting galaxies whose r-filter magnitude was above $-19$ (VERIFY).\\
+The principal method used in Jones et al. \cite{jones1} analyses the
+dependence of the Schechter parameters on the cosmological
+environment. To obtain a quantification of said cosmological
+environment, they calculated for each galaxy in the studied survey the
+projected distance in the sky to the third nearest neighbor,
+filtrating candidate neighbors by its radial velocity relative to the
+reference galaxy. According to Hubble's law, this effectively
+restricts the candidate galaxies to a smaller radial range, reducing
+apparent closer galaxies arising from the projection method. The
+radial relative velocity cut was chosen to be $450km/s$. Furthermore,
+a photometrics pre-selection was performed, selecting galaxies whose
+r-filter magnitude was above $-19$ (VERIFY).\\
 
-Once quantified the environment with the distance to the 3rd nearest neighbor definition for each galaxy in their post-selected survey they divided the group in four quartiles according this quantity.
-For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained.
-The analysis was specifically performed over the Schechter parameters of the Knee-mass and the faint-end slope.
-\\
+Once quantified the environment with the distance to the 3rd nearest
+neighbor definition for each galaxy in their post-selected survey they
+divided the group in four quartiles according this quantity. For each
+quartile, the respective HIMF was calculated, and with this, a
+Schechter fit was obtained. The analysis was specifically performed
+over the Schechter parameters of the Knee-mass and the faint-end
+slope. \\
 
-In dark matter cosmological simulations, access to the information is istantaneous and at no cost.
-However, as we want to replicate as closely as possible the method effectuated by Jones et.
-al \cite{jones1}, we also calculate the projected distance in the simulation and take the same projected velocity cut according to a specified point of view.
-Even when we could easily calculate the distance to the third nearest neighbor we take into account these observational simplifications, to make our study as comparable as possible to that of Jones et al.
-\cite{jones1}.\\
+In dark matter cosmological simulations, access to the information is
+istantaneous and at no cost. However, as we want to replicate as
+closely as possible the method effectuated by Jones et. al
+\cite{jones1}, we also calculate the projected distance in the
+simulation and take the same projected velocity cut according to a
+specified point of view. Even when we could easily calculate the
+distance to the third nearest neighbor we take into account these
+observational simplifications, to make our study as comparable as
+possible to that of Jones et al. \cite{jones1}.\\
 
@@
 
-% The best way to enter references is to use BibTeX:
-
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-\begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-Others S., 2012, Journal of Interesting Stuff, 17, 198
-\end{thebibliography}
+\bibliographystyle{mnras}
+\bibliography{references}
 
@@
 
-% Don't change these lines
 \bsp	% typesetting comment
 \label{lastpage}
+
 \end{document}

### 2017-08-31 Paper/paper.tex
cut long paragraphs

@@
 \section{Illustris Simulation}
-Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.\\
+Illustris-1, also known simply as Illustris, is a highly resolved
+cosmological simulation which reproduces large-scale statistical
+features of the Universe, such as the galaxy population of massive
+clusters, as well as small-scale properties such as the morphology of
+galaxies and detailed values for their stellar and gas content.\\
 
@@
 The $\Lambda \text{CDM}$ cosmology of this run follows: $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
-^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy Probe (WMAP)-9 \cite{AnisotropyProbe}.
-Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation.
-\\
+^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy
+Probe (WMAP)-9 \cite{AnisotropyProbe}. Illustris has a constant
+spatial resolution of $1.4\text{kpc}$ for DM particles in comoving
+units, and for baryonic particles it has the same spatial resolution
+of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$
+in physical units for the rest of the simulation. \\
 
-The evolution in time was performed with the hydrodynamic code AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach.
-Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs.
-Specifically, the physics followed by this model includes energetic feedback from supermassive black holes and supernovae, as well as stellar evolution and chemical enrichment.
-This level of detail in Illustris is advantageous for the analysis of the effect of the environment  in galactic barionic properties and is hard to find among other simulations, i.e.
-post-processed runs with semi-analytical models which do not directly simulate baryons.(Expand) Describe Arepo a little bit more\\
+The evolution in time was performed with the hydrodynamic code AREPO
+\cite{arepo}, which combines a moving Voronoi tessellation with the
+finite volume approach. Included in the evolution algorithm, there are
+galaxy formation models which account for the evolution of stars and
+SMBHs. Specifically, the physics followed by this model includes
+energetic feedback from supermassive black holes and supernovae, as
+well as stellar evolution and chemical enrichment. This level of
+detail in Illustris is advantageous for the analysis of the effect of
+the environment  in galactic barionic properties and is hard to find
+among other simulations, i.e. post-processed runs with semi-analytical
+models which do not directly simulate baryons.(Expand) Describe Arepo
+a little bit more\\
 
-The output of this simultaion consists of 136 snapshots where 61 of them were taken at $z < 3$ spaced with a cosmological scale factor $\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$ with spacing $\Delta a \approx 0.01$.
-Each snapshot was post-processed with a modified version of FOF \cite{FOF} to identify DM haloes with more than 32 particles using a linking length of 0.2 times the mean particle separation each of which is analyzed with the SUBFIND algorithm \cite{subfind} to generate, at z=0, 7,713,601 halos (FOF) and 4,366,546 (sub)halo catalogues with their respective characterization properties.
-\\
+The output of this simultaion consists of 136 snapshots where 61 of
+them were taken at $z < 3$ spaced with a cosmological scale factor
+$\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$
+with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed
+with a modified version of FOF \cite{FOF} to identify DM haloes with
+more than 32 particles using a linking length of 0.2 times the mean
+particle separation each of which is analyzed with the SUBFIND
+algorithm \cite{subfind} to generate, at z=0, 7,713,601 halos (FOF)
+and 4,366,546 (sub)halo catalogues with their respective
+characterization properties. \\
 
@@
 
-The principal purpose of this work is to verify if the results obtained observationally by Jones et al.
-\cite{jones1} are supported by a similar analysis in the cosmological simulation Illustris.
-For this purpose, we want to adaptate the observational method as closely as posible for it to work on computational data.\\
+The principal purpose of this work is to verify if the results
+obtained observationally by Jones et al. \cite{jones1} are supported
+by a similar analysis in the cosmological simulation Illustris. For
+this purpose, we want to adaptate the observational method as closely
+as posible for it to work on computational data.\\
 
@@
 
-Mass resolution reduces the size of the sample galaxies and this complicates the process of photometrics pre-selection.
-This selection significatively reduces the size of the galaxy set which is already smaller than normal due to the resolution cut.
-This made impossible a Schechter fit to the obtained mass functions given that the associated logarithmic errors became extremely large.
-For this reason, we omit the photometrics pre-selection which is the only feature that our analysis misses with respect to the one from \cite{jones1}.\\
+Mass resolution reduces the size of the sample galaxies and this
+complicates the process of photometrics pre-selection. This selection
+significatively reduces the size of the galaxy set which is already
+smaller than normal due to the resolution cut. This made impossible a
+Schechter fit to the obtained mass functions given that the associated
+logarithmic errors became extremely large. For this reason, we omit
+the photometrics pre-selection which is the only feature that our
+analysis misses with respect to the one from \cite{jones1}.\\
 
 \subsection{The cosmic web method}
-To complement the analysis performed with the third nearest neighbor method for the classification of environments, we chose a complementary method of completely different nature to verify even more the results from Jones et al..
-The method chosen here was the one developed by Forero et al.
-\cite{forero1}, which uses the Hessian of the gravitational potential obtained from the DM field to classify galaxies into (conveniently) four morphological environments.\\
+To complement the analysis performed with the third nearest neighbor
+method for the classification of environments, we chose a
+complementary method of completely different nature to verify even
+more the results from Jones et al.. The method chosen here was the one
+developed by Forero et al. \cite{forero1}, which uses the Hessian of
+the gravitational potential obtained from the DM field to classify
+galaxies into (conveniently) four morphological environments.\\
 
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesGas.png}
-    \caption{\textbf{Upper side}: Schechter fits of each gas mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each gas mass
+      function for each environmental quartile using the 3rd nearest
+      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
+      the faint end slope $\alpha$ values obtained from the Schechter
+      fits for each curve shown above.} 
     \label{fig:quartilesGas}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_Gas.png}
-    \caption{\textbf{Upper side}: Schechter fits of each gas mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each gas mass
+      function for each morphological environment characterized by the
+      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
+      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
+      obtained from the Schechter fits for each curve shown above.} 
     \label{fig:TwebGas}
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesDM.png}
-    \caption{\textbf{Upper side}: Schechter fits of each DM mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each DM mass
+      function for each environmental quartile using the 3rd nearest
+      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
+      the faint end slope $\alpha$ values obtained from the Schechter
+      fits for each curve shown above.} 
     \label{fig:quartilesDM}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_DM.png}
-    \caption{\textbf{Upper side}: Schechter fits of each DM mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each DM mass
+      function for each morphological environment characterized by the
+      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
+      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
+      obtained from the Schechter fits for each curve shown above.} 
     \label{fig:TwebDM}
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesSellar.png}
-    \caption{\textbf{Upper side}: Schechter fits of each stellar mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each stellar mass
+      function for each environmental quartile using the 3rd nearest
+      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
+      the faint end slope $\alpha$ values obtained from the Schechter
+      fits for each curve shown above.} 
     \label{fig:quartilesStellar}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_Stellar.png}
-    \caption{\textbf{Upper side}: Schechter fits of each stellar mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each stellar mass
+      function for each morphological environment characterized by the
+      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
+      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
+      obtained from the Schechter fits for each curve shown above.} 
     \label{fig:TwebStellar}
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesBH.png}
-    \caption{\textbf{Upper side}: Schechter fits of each BH mass function for each environmental quartile using the 3rd nearest neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each BH mass
+      function for each environmental quartile using the 3rd nearest
+      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
+      the faint end slope $\alpha$ values obtained from the Schechter
+      fits for each curve shown above.} 
     \label{fig:quartilesBH}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_BH.png}
-    \caption{\textbf{Upper side}: Schechter fits of each BH mass function for each morphological environment characterized by the T-Web algorithm proposed by Forero et al.\textbf{Down side}: Knee-mass $m_\ast$ and the faint end slope $\alpha$ values obtained from the Schechter fits for each curve shown above.}
+    \caption{\textbf{Upper side}: Schechter fits of each BH mass
+      function for each morphological environment characterized by the
+      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
+      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
+      obtained from the Schechter fits for each curve shown above.} 
     \label{fig:TwebBH}

### 2017-09-03 Illustris_Run/Code/C_libs/environment.c
Fully functional everything

@@ -120,7 +120,7 @@ int main(int argc, char **argv){
   int i,j,k;
   int numb;
 
-#pragma omp parallel for   
+#pragma omp parallel for private(i,j,k) 
   for( numb = 0; numb < (int) (res*res*res); numb++){
   //for( i = 0; i < res; i++){
     //for( j = 0; j < res; j++){
@@ -130,7 +130,7 @@ int main(int argc, char **argv){
          i = (int)(((int)(numb/res))/res);
          
          List* actual = (gridG[i][j][k])->next;
-         printf("%d_%d_%d_\n",i,j,k);
+         printf("%d_%d_%d_%d\n",i,j,k,(int)(res*res*i+res*j+k));
 
         do{
 
@@ -372,7 +372,6 @@ void get_Env(int j, int hx, int hy, int hz){
            actual = actual->next;
 
          }while(actual != 0);
-
 
          //printf("_%d_%d_%d_\n",ix,iy,iz);
          iz = rPBC(iz+1);

### 2017-09-03 Illustris_Run/Code/Py_libs/Illustris_Cluster.py

@@ -25,9 +25,11 @@ for path,filename,massfn in zip([path1,path2,path3],filenames,massFilenames):
     pos  = subSn.SubhaloPos
     vel  = subSn.SubhaloVel
     mass = subSn.SubhaloMassType
-
+    sph  = subSn.SubhaloStellarPhotometrics[:,5]
     # Have into account only subhalos with mass
-    ind, = np.where(mass.T[0]>0)
+    #for mag in sph[np.where(sph.T>0)[0]]:
+    #    print(mag)
+    ind, = np.where((mass.T[0]>0) & (sph < 0))
     print(len(pos))
     pos  = pos[ind]
     vel  = vel[ind]

### 2017-09-03 Illustris_Run/Code/Py_libs/read_tweb.py

@@ -1,7 +1,7 @@
 import struct
 import numpy as np
-import matplotlib.pyplot as plt
-import illustris_python as il
+#import matplotlib.pyplot as plt
+#import illustris_python as il
 import time
 
 def read_CIC_scalar(filename):
@@ -77,47 +77,47 @@ def getEnv(x,y,z):
 def getGalaxies(basePath,cut):
     start_time = time.time()
     # Selects the fields to load for subhalos
-    fields = ['SubhaloCM','SubhaloStellarPhotometrics','SubhaloMassType']
+    #fields = ['SubhaloCM','SubhaloStellarPhotometrics','SubhaloMassType']
     # Loads subhalos to variable g
-    g = il.groupcat.loadSubhalos(basePath,135,fields=fields)
+    g = np.loadtxt(basePath,delimiter=',')
 
     # Counts the galaxies by magnitude and not null gas mass
     # filter the galaxies for its photometrics (only rband < -19)
-    print "Number of galaxies before: " + str(g['count'])
-    ngalaxies = len(np.where((g[fields[2]][:,0]!=0)*(g[fields[1]][:,5]<cut))[0])
-    print "Number of galaxies after: " + str(ngalaxies)
+    print "Number of galaxies: " + str(len(g))
+    ngalaxies = len(g)
+    #print "Number of galaxies after: " + str(ngalaxies)
 
     # Creates arrays for the candidate galaxies and fills it
     Galaxies = np.array([[0.0,0.0,0.0] for i in range(ngalaxies)])
     i = 0
     imax = 0
-    for j in range(g['count']):
-        if( (g['SubhaloMassType'][j][0] != 0) and ((g[fields[1]][j][5] < cut)) ):
+    for j in range(ngalaxies):
+        #if( (g['SubhaloMassType'][j][0] != 0) and ((g[fields[1]][j][5] < cut)) ):
         #if(True):
-            #print g['SubhaloMassType'][j][0]
-            ix = int(g['SubhaloCM'][j][0]/delx)
-            iy = int(g['SubhaloCM'][j][1]/delx)
-            iz = int(g['SubhaloCM'][j][2]/delx)
-            ex = eigen1[ix,iy,iz]
-            ey = eigen2[ix,iy,iz]
[…]

### 2017-10-17 Paper/paper.tex
changes

@@
 Illustris-1, also known simply as Illustris, is a highly resolved
-cosmological simulation which reproduces large-scale statistical
+cosmological simulation. It reproduces large-scale statistical
 features of the Universe, such as the galaxy population of massive
@@
 detail in Illustris is advantageous for the analysis of the effect of
-the environment  in galactic barionic properties and is hard to find
+the environment in barionic properties of galaxies. This level of resolution is hard to find
 among other simulations, i.e. post-processed runs with semi-analytical
-models which do not directly simulate baryons.(Expand) Describe Arepo
-a little bit more\\
+models which do not directly simulate baryons.(Expand) Describe Arepo more\\
 
-The output of this simultaion consists of 136 snapshots where 61 of
+The output of this simultaion consists of 136 snapshots. 61 of
 them were taken at $z < 3$ spaced with a cosmological scale factor
-$\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$
+$\Delta a \approx 0.02$. The remaining 75 were taken at $z > 3$
 with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed
@@
 more than 32 particles using a linking length of 0.2 times the mean
-particle separation each of which is analyzed with the SUBFIND
-algorithm \cite{subfind} to generate, at z=0, 7,713,601 halos (FOF)
+particle separation. Each output group from the 7,713,601 post-processed halos (FOF) is analyzed with the SUBFIND
+algorithm \cite{subfind} to generate, at z=0,
 and 4,366,546 (sub)halo catalogues with their respective
@@
 obtained observationally by Jones et al. \cite{jones1} are supported
-by a similar analysis in the cosmological simulation Illustris. For
-this purpose, we want to adaptate the observational method as closely
-as posible for it to work on computational data.\\
+by a similar analysis in the cosmological simulation Illustris.
+Specifically, we focus on the (small-scale) environment definition of the $3^{rd}$ nearest neighbor, which we want to adapt as closely as possible to our computational application.\\
 
-\subsection{The $3^{rd}$ nearest neighbor method}
+\subsection{The $3^{rd}$ nearest neighbor definition of environment}
 
-The principal method used in Jones et al. \cite{jones1} analyses the
+Jones et al. \cite{jones1} analyses the
 dependence of the Schechter parameters on the cosmological
@@
 projected distance in the sky to the third nearest neighbor,
-filtrating candidate neighbors by its radial velocity relative to the
+filtrating candidate neighbors by their radial velocity relative to the
 reference galaxy. According to Hubble's law, this effectively
@@
 apparent closer galaxies arising from the projection method. The
-radial relative velocity cut was chosen to be $450km/s$. Furthermore,
+radial relative velocity cut was chosen to be $450km/s$. In addition to this,
 a photometrics pre-selection was performed, selecting galaxies whose
@@
 Once quantified the environment with the distance to the 3rd nearest
-neighbor definition for each galaxy in their post-selected survey they
-divided the group in four quartiles according this quantity. For each
+neighbor definition they divided the group in four quartiles according this quantity. For each
 quartile, the respective HIMF was calculated, and with this, a
@@
 over the Schechter parameters of the Knee-mass and the faint-end
-slope. \\
+slope. (Some observational adjustments for the Schechter functions were performed)  \\
 
-In dark matter cosmological simulations, access to the information is
-istantaneous and at no cost. However, as we want to replicate as
-closely as possible the method effectuated by Jones et. al
-\cite{jones1}, we also calculate the projected distance in the
-simulation and take the same projected velocity cut according to a
-specified point of view. Even when we could easily calculate the
-distance to the third nearest neighbor we take into account these
-observational simplifications, to make our study as comparable as
-possible to that of Jones et al. \cite{jones1}.\\
-
-However, as Illustris is a cosmological simulation, it is subject to numerical resolution biases, being the most important, the mass resolution biases.
-Each mass considered here is subject directly or indirectly to a mass resolution, and the effect it causes is specially evident in the produced mass functions.
-We used Illustris-3, which is a less resoluted copy of Illustris-1, to verify that the effect on the mass functions is indeed caused by mass resolution.
+As we want to replicate as closely as possible the method effectuated by Jones et. al
+\cite{jones1}, we use the same specifications to calculare the environment.
+ We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
+ However, we do not perform it directly on HIMFs because this would require some extense calculations.
+  We take the gas mass function as a first approximation.
+ As Illustris is a cosmological simulation, it is subject to resolution biases.
+The most important bias in this study is related to the minimum mass of discrete elements in the simulation. 
+Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions. 
+We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \fig{resolution effects}. 
 Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
@@
 
-Mass resolution reduces the size of the sample galaxies and this
-complicates the process of photometrics pre-selection. This selection
-significatively reduces the size of the galaxy set which is already
-smaller than normal due to the resolution cut. This made impossible a
-Schechter fit to the obtained mass functions given that the associated
-logarithmic errors became extremely large. For this reason, we omit
-the photometrics pre-selection which is the only feature that our
-analysis misses with respect to the one from \cite{jones1}.\\
+\subsection{The cosmic web method}
+To complement and verify the analysis performed with the third nearest neighbor
+method, we chose a complementary method of completely different nature. 
+The chosen method was developed by Forero et al. \cite{forero1}. 
+It uses the Hessian \ref{eq:hessian} of
+the gravitational potential obtained from the DM density field to classify
+galaxies into four morphological environments.\\
 
-\subsection{The cosmic web method}
-To complement the analysis performed with the third nearest neighbor
-method for the classification of environments, we chose a
-complementary method of completely different nature to verify even
-more the results from Jones et al.. The method chosen here was the one
-developed by Forero et al. \cite{forero1}, which uses the Hessian of
-the gravitational potential obtained from the DM field to classify
-galaxies into (conveniently) four morphological environments.\\
+\begin{equation}
+E =  mc^2
+\label{eq:hessian}
+\end{equation}
+
+Specifically, we diagonalize the Hessian matrix obtaining three eigenvalues. 
+These eigenvalues determine the concavity of the gravitational potential on the principal axes, at each point.
+We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$.
+Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to expand? in the respective eigenaxes, and viceversa. 
+With this characterization, clusters, sheets, fillaments and voids can be defined with the number of axes above $\lambda$.
+Forero et. al. found in \cite{forero1} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\
+
+With these specifications, we could obtain mass functions for galaxies belonging to clusters, fillaments and sheets.
+The amount of galaxies belonging to voids was strongly affected by the mentioned mass cuts and could not produce reasonable mass functions to analyze.
 
@@
     \caption{\textbf{Upper side}: Schechter fits of each gas mass
-      function for each environmental quartile using the 3rd nearest
+      function for each environmental quartile (tendence) using the 3rd nearest
       neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesDM.png}
-    \caption{\textbf{Upper side}: Schechter fits of each DM mass
-      function for each environmental quartile using the 3rd nearest
-      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
-      the faint end slope $\alpha$ values obtained from the Schechter
-      fits for each curve shown above.} 
+    \caption{Similar to figure \ref{fig:quartilesGas} using DM.} 
     \label{fig:quartilesDM}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_DM.png}
-    \caption{\textbf{Upper side}: Schechter fits of each DM mass
-      function for each morphological environment characterized by the
-      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
-      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
-      obtained from the Schechter fits for each curve shown above.} 
+    \caption{Similar to figure \ref{fig:TwebGas} using DM.} 
     \label{fig:TwebDM}
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesSellar.png}
-    \caption{\textbf{Upper side}: Schechter fits of each stellar mass
-      function for each environmental quartile using the 3rd nearest
-      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
-      the faint end slope $\alpha$ values obtained from the Schechter
-      fits for each curve shown above.} 
+    \caption{Similar to figure \ref{fig:quartilesGas} using stellar mass} 
     \label{fig:quartilesStellar}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_Stellar.png}
-    \caption{\textbf{Upper side}: Schechter fits of each stellar mass
-      function for each morphological environment characterized by the
-      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
-      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
-      obtained from the Schechter fits for each curve shown above.} 
+    \caption{Similar to figure \ref{fig:TwebGas} using stellar mass} 
     \label{fig:TwebStellar}
@@
 	\includegraphics[width=\columnwidth]{./pics/quartilesBH.png}
-    \caption{\textbf{Upper side}: Schechter fits of each BH mass
-      function for each environmental quartile using the 3rd nearest
-      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
-      the faint end slope $\alpha$ values obtained from the Schechter
-      fits for each curve shown above.} 
+    \caption{Similar to figure \ref{fig:quartilesGas} using BHs mass.} 
     \label{fig:quartilesBH}
@@
 	\includegraphics[width=\columnwidth]{./pics/T-Web_BH.png}
-    \caption{\textbf{Upper side}: Schechter fits of each BH mass
-      function for each morphological environment characterized by the
-      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
-      Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
-      obtained from the Schechter fits for each curve shown above.} 
+    \caption{Similar to figure \ref{fig:TwebGas} using BHs mass.} 
     \label{fig:TwebBH}

### 2017-10-18 Paper/paper.tex
Some details

@@
 
-The principal purpose of this work is to verify if the results
-obtained observationally by Jones et al. \cite{jones1} are supported
-by a similar analysis in the cosmological simulation Illustris.
-Specifically, we focus on the (small-scale) environment definition of the $3^{rd}$ nearest neighbor, which we want to adapt as closely as possible to our computational application.\\
+The principal purpose of this work is to verify if the results obtained observationally by Jones et al.
+\cite{jones1} are supported by a similar analysis in the cosmological simulation Illustris.
+Specifically, we focus on the \textit{local} environment definition of the $3^{rd}$ nearest neighbor (NN), which we want to adapt as closely as possible to our computational application.\\
 
@@
 
-Jones et al. \cite{jones1} analyses the
-dependence of the Schechter parameters on the cosmological
-environment. To obtain a quantification of said cosmological
-environment, they calculated for each galaxy in the studied survey the
-projected distance in the sky to the third nearest neighbor,
-filtrating candidate neighbors by their radial velocity relative to the
-reference galaxy. According to Hubble's law, this effectively
-restricts the candidate galaxies to a smaller radial range, reducing
-apparent closer galaxies arising from the projection method. The
-radial relative velocity cut was chosen to be $450km/s$. In addition to this,
-a photometrics pre-selection was performed, selecting galaxies whose
-r-filter magnitude was above $-19$ (VERIFY).\\
+Jones et al. \cite{jones1} analyze the dependence of the HIMF's Schechter parameters on the cosmological environment.
 
-Once quantified the environment with the distance to the 3rd nearest
-neighbor definition they divided the group in four quartiles according this quantity. For each
-quartile, the respective HIMF was calculated, and with this, a
-Schechter fit was obtained. The analysis was specifically performed
-over the Schechter parameters of the Knee-mass and the faint-end
-slope. (Some observational adjustments for the Schechter functions were performed)  \\
+They used the SDSS \cite{SDSS} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
 
-As we want to replicate as closely as possible the method effectuated by Jones et. al
-\cite{jones1}, we use the same specifications to calculare the environment.
+This SDSS catalogue was constituted of pre-selected galaxies brighter than $M_r = -18.9$.
+
+To obtain a quantification the environment, for each reference galaxy in ALFALFA they found the projected distance in the sky to the third NN belonging to the pre-selected SDSS catalogue.
+
+This projected distance in the sky defines a numeric-surface density for each reference galaxy.
+
+They filtrated candidate neighbors by their radial velocity relative to the reference galaxy which had to be within $450km/s$.
+
+According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the use of projected distances. \\
+
+Once quantified the environment for each ALFALFA galaxy with the distance to the 3rd NN definition, they divided the group in four quartiles according this quantity.
+
+For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained.
+
+The analysis was specifically performed over the Schechter parameters of the Knee-mass $M^*$ and the faint-end slope $\alpha$. \\
+
+As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{jones1}, we use the same specifications to calculate the environment.
+
 We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
- However, we do not perform it directly on HIMFs because this would require some extense calculations.
-  We take the gas mass function as a first approximation.
- As Illustris is a cosmological simulation, it is subject to resolution biases.
+
+We do not perform the study directly on HIMFs because this would require some extense calculations although we take the gas mass function as a first approximation.\\
+
+As Illustris is a cosmological simulation, it is subject to resolution and numerical biases.
+
 The most important bias in this study is related to the minimum mass of discrete elements in the simulation.
+
 Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions.
-We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \fig{resolution effects}. 
+
+We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \ref{fig:resolution effects}.
+
 Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
-This mass cut has no aparent systematical way to be calculated and therefore, we performed the cut having into account the performance of the respective Schechter fit.\\
+
+This mass cut has no apparent systematical way to be calculated and therefore, we choose it having into account the performance of the respective Schechter fit.\\
 
 \subsection{The cosmic web method}
-To complement and verify the analysis performed with the third nearest neighbor
-method, we chose a complementary method of completely different nature. 
+To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature.
+
 The chosen method was developed by Forero et al. \cite{forero1}.
-It uses the Hessian \ref{eq:hessian} of
-the gravitational potential obtained from the DM density field to classify
-galaxies into four morphological environments.\\
+
+It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the DM density field to classify galaxies into four morphological environments.\\
 
@@
 Specifically, we diagonalize the Hessian matrix obtaining three eigenvalues.
+
 These eigenvalues determine the concavity of the gravitational potential on the principal axes, at each point.
 We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$.
+
 Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to expand? in the respective eigenaxes, and viceversa.
+
 With this characterization, clusters, sheets, fillaments and voids can be defined with the number of axes above $\lambda$.
+
 Forero et. al. found in \cite{forero1} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/quartilesGas.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesGas.png}
     \caption{\textbf{Upper side}: Schechter fits of each gas mass
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/T-Web_Gas.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_Gas.png}
     \caption{\textbf{Upper side}: Schechter fits of each gas mass
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/quartilesDM.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesDM.png}
     \caption{Similar to figure \ref{fig:quartilesGas} using DM.} 
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/T-Web_DM.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_DM.png}
     \caption{Similar to figure \ref{fig:TwebGas} using DM.} 
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/quartilesSellar.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesSellar.png}
     \caption{Similar to figure \ref{fig:quartilesGas} using stellar mass} 
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/T-Web_Stellar.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_Stellar.png}
     \caption{Similar to figure \ref{fig:TwebGas} using stellar mass} 
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/quartilesBH.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesBH.png}
     \caption{Similar to figure \ref{fig:quartilesGas} using BHs mass.} 
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/T-Web_BH.png}
+	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_BH.png}
     \caption{Similar to figure \ref{fig:TwebGas} using BHs mass.} 

### 2017-10-26 Paper/paper.tex
Schechter - MF section

@@
 \section{Illustris Simulation}
-Illustris-1, also known simply as Illustris, is a highly resolved
+Illustris-1, also known as Illustris, is a highly resolved
 cosmological simulation. It reproduces large-scale statistical
@@
 
-\section{The method}
+\section{The methodology}
+
+\subsection{ Characterizing Mass Functions}
+A mass function is the number density $n(M)$ of objects of determined mass $M$.
+Due to the large range of orders of magnitud in which these quantities span, the mass function is often represented in logarithmic scales on both sides. 
+The discretization of these mass functions is simply the histogram of the logarithmic masses of the studied group of objects. 
+In Illustris, as in all simulations, we have clear determination of volumes.
+This volume is constant over all the sample of galaxies studied and is to be taken the constant volume of the simulation $V = \left(106.5\text{Mpc}\right)^3$.
+In this sense, the relation expressed by a mass function is
+
+\begin{equation}
+n(M)Vd\log{(M)} =  dN
+\end{equation}
+
+To characterize specific properties of these mass functions, we use the Press-Schechter function \ref{eq:Schechter}. 
+It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
+Although its ansatz has been demonstrated to be inaccurate for our observable universe \cite{inaccurateSchechter}, the final expression is very well fitted to the mass functions of the local universe \cite{wellfitSchechter}.\\
+
+\begin{equation}
+n\left( M \right) = n_*\left( \frac{M}{M_*} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_*}\right)}
+\label{eq:Schechter}
+\end{equation}
+
+The Schechter function \ref{eq:Schechter} is fully defined by the three parameters $(n_*,M_*,\alpha)$. 
+The number density factor $n_*$ is just a normalization factor which vary depending on the studied system. 
+The mass scale factor $M_*$ may be interpreted as the mass that separates the power-law regimen $M \ll M_*$ and the exponential regimen $M \gg M_*$. 
+This transition graphically resemnles a knee, which is the reason why $M_*$ is referred as the knee-mass.
+The faint-end slope $\alpha$ is directly related to the exponent of the power-law at the low-mass regime.
+In logarithmic scales, it is clearly interpreted as the slope of the low-mass regime.\\
+
+We characterize each mass function with a Schechter
+function \ref{eq:schechter}. It is . These parameters and their
+respective estimated errors are determined with a MCMC fit
+applied directly to the MF.\\
 
@@
 
-\subsection{The $3^{rd}$ nearest neighbor definition of environment}
+\subsection{Defining the environment}
+
+\subsubsection{The $3^{rd}$ nearest neighbor definition of environment}
 
@@
 
-\subsection{The cosmic web method}
+\subsubsection{The cosmic web method}
 To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature.

### 2017-10-27 Paper/paper.tex
ASD

@@
 
-We characterize each mass function with a Schechter
-function \ref{eq:schechter}. It is . These parameters and their
-respective estimated errors are determined with a MCMC fit
-applied directly to the MF.\\
+\subsection{Defining the environment}
 
-The principal purpose of this work is to verify if the results obtained observationally by Jones et al.
-\cite{jones1} are supported by a similar analysis in the cosmological simulation Illustris.
-Specifically, we focus on the \textit{local} environment definition of the $3^{rd}$ nearest neighbor (NN), which we want to adapt as closely as possible to our computational application.\\
+Given the current interest in the study of the dependence of observational HIMFs on the environment and the wide difference of the conclusions of these studies, the main scope of this work is to verify if the any results obtained observationally are supported by a similar analysis in the cosmological simulation Illustris.\\
 
-\subsection{Defining the environment}
+For this purpose, we take two approaches to analyze the dependence of mass functions on environment. 
+On one hand, to make our study observationally-comparable, we follow the 3rd nearest neighbor (3NN) definition of environment proposed by Jones et al. \cite{Jones2016}. 
+On the other hand, to confirm our results, we use a computational definition of environment (T-Web) of completely different nature proposed by Forero et al. \cite{Forero2009}.
 
@@
 
-Jones et al. \cite{jones1} analyze the dependence of the HIMF's Schechter parameters on the cosmological environment.
+Jones et al. \cite{jones1} the SDSS \cite{SDSS2011} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
+This SDSS catalogue was chosen to be optically-selected and volume-limited to account for apparent lonely galaxies in ALFALFA with increasinf distance. 
+For this reason, they pre-selected galaxies brighter than $M_r = -18.9$ in this survey.
 
-They used the SDSS \cite{SDSS} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
-
-This SDSS catalogue was constituted of pre-selected galaxies brighter than $M_r = -18.9$.
-
-To obtain a quantification the environment, for each reference galaxy in ALFALFA they found the projected distance in the sky to the third NN belonging to the pre-selected SDSS catalogue.
-
+To quantify the environment , for each reference galaxy in ALFALFA, they calculated the projected distance in the sky to the third nearest neighbor belonging to the pre-selected SDSS catalogue.
 This projected distance in the sky defines a numeric-surface density for each reference galaxy.
-
-They filtrated candidate neighbors by their radial velocity relative to the reference galaxy which had to be within $450km/s$.
-
+To do so, first, they filtrated candidate neighbors by their radial velocity relative to the reference galaxy which had to be within $450km/s$.
 According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the use of projected distances. \\

### 2017-10-27 Paper/paper.tex
ASD

@@
 The Schechter function \ref{eq:Schechter} is fully defined by the three parameters $(n_*,M_*,\alpha)$. 
-The number density factor $n_*$ is just a normalization factor which vary depending on the studied system. 
+The number density factor $n_*$ is just a normalization factor which varies depending on the studied system. 
 The mass scale factor $M_*$ may be interpreted as the mass that separates the power-law regimen $M \ll M_*$ and the exponential regimen $M \gg M_*$. 
@@
 On one hand, to make our study observationally-comparable, we follow the 3rd nearest neighbor (3NN) definition of environment proposed by Jones et al. \cite{Jones2016}. 
-On the other hand, to confirm our results, we use a computational definition of environment (T-Web) of completely different nature proposed by Forero et al. \cite{Forero2009}.
+On the other hand, to confirm our results, we use a computational and theoretical definition of environment (T-Web) of completely different nature proposed by Forero et al. \cite{Forero2009}.
 
@@
 Once quantified the environment for each ALFALFA galaxy with the distance to the 3rd NN definition, they divided the group in four quartiles according this quantity. 
-
 For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained. 
-
-The analysis was specifically performed over the Schechter parameters of the Knee-mass $M^*$ and the faint-end slope $\alpha$. \\
+%The analysis was specifically performed over the Schechter parameters of the Knee-mass $M^*$ and the faint-end slope $\alpha$. \\
 
 As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{jones1}, we use the same specifications to calculate the environment.
-
 We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
-
-We do not perform the study directly on HIMFs because this would require some extense calculations although we take the gas mass function as a first approximation.\\
+We do not perform the study directly on HIMFs because this would require some extense calculations. We take the gas mass function as a first approximation.\\
 
 As Illustris is a cosmological simulation, it is subject to resolution and numerical biases.
-
 The most important bias in this study is related to the minimum mass of discrete elements in the simulation.
-
 Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions. 
-
 We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \ref{fig:resolution effects}. 
-
 Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
-
 This mass cut has no apparent systematical way to be calculated and therefore, we choose it having into account the performance of the respective Schechter fit.\\
@@
 To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature. 
-
 The chosen method was developed by Forero et al. \cite{forero1}. 
-
 It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the DM density field to classify galaxies into four morphological environments.\\
@@
 Specifically, we diagonalize the Hessian matrix obtaining three eigenvalues. 
-
 These eigenvalues determine the concavity of the gravitational potential on the principal axes, at each point.
 We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$.
-
 Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to expand? in the respective eigenaxes, and viceversa. 
-
 With this characterization, clusters, sheets, fillaments and voids can be defined with the number of axes above $\lambda$.
-
-Forero et. al. found in \cite{forero1} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\
+Forero et. al. found in \cite{forero2009} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\
 
@@
 worry about the exact layout, which will be handled by the publishers.
-
 Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as

### 2017-10-27 Paper/paper.tex
some references, unexpected format

@@
 
-\cite{Tweb}.
+\cite{Forero2009}.
 
@@
 The evolution in time was performed with the hydrodynamic code AREPO
-\cite{arepo}, which combines a moving Voronoi tessellation with the
+\cite{Arepo}, which combines a moving Voronoi tessellation with the
 finite volume approach. Included in the evolution algorithm, there are
@@
 particle separation. Each output group from the 7,713,601 post-processed halos (FOF) is analyzed with the SUBFIND
-algorithm \cite{subfind} to generate, at z=0,
+algorithm \cite{SUBFIND} to generate, at z=0,
 and 4,366,546 (sub)halo catalogues with their respective
@@
 
+To obtain the Schechter parameters that characterize each numerical mass function, we used MCMC to obtain the fit with best likelihood. 
+With this, we could also ...\\
+
+As Illustris is a cosmological simulation, it is subject to resolution and numerical biases.
+The most important bias in this study is related to the minimum mass of discrete elements in the simulation.
+Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions. 
+We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \ref{fig:resolution effects}. 
+Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
+This mass cut has no apparent systematical way to be calculated and therefore, we choose it having into account the performance of the respective Schechter fit.\\
+
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{./pics/MassResolution.png}
+    \caption{The effect on mass resolution on mass functions of Illustris-1,2,3. (Masses have units $10^{10}M_\odot$)} 
+    \label{fig:resolution effects}
+\end{figure}
+
 \subsection{Defining the environment}
@@
 
-Jones et al. \cite{jones1} the SDSS \cite{SDSS2011} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
+Jones et al. \cite{Jones2016} the SDSS \cite{SDSS2011} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
 This SDSS catalogue was chosen to be optically-selected and volume-limited to account for apparent lonely galaxies in ALFALFA with increasinf distance. 
-For this reason, they pre-selected galaxies brighter than $M_r = -18.9$ in this survey.
+For this reason, they pre-selected galaxies brighter than $M_r = -18.9$ in this survey.\\
 
@@
 
-As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{jones1}, we use the same specifications to calculate the environment.
+As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{Jones2016}, we use the same specifications to calculate the environment.
 We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
@@
 
-As Illustris is a cosmological simulation, it is subject to resolution and numerical biases.
-The most important bias in this study is related to the minimum mass of discrete elements in the simulation.
-Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions. 
-We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \ref{fig:resolution effects}. 
-Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
-This mass cut has no apparent systematical way to be calculated and therefore, we choose it having into account the performance of the respective Schechter fit.\\
-
 \subsubsection{The cosmic web method}
 To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature. 
-The chosen method was developed by Forero et al. \cite{forero1}. 
-It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the DM density field to classify galaxies into four morphological environments.\\
+The chosen method was developed by Forero et al. \cite{Forero2009}. 
+It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the smoothened DM density field to classify galaxies into four morphological environments.\\
 
@@
 
-Specifically, we diagonalize the Hessian matrix obtaining three eigenvalues. 
-These eigenvalues determine the concavity of the gravitational potential on the principal axes, at each point.
+Specifically, we diagonalize the Hessian matrix of the gravitational potential $\phi$ obtaining three eigenvalues. 
+This matrix encodes the local curvature of the gravitational potential. 
+Specifically, these eigenvalues determine the concavity of $\phi$ on the principal axes, at each point. 
 We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$. 
-Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to expand? in the respective eigenaxes, and viceversa. 
-With this characterization, clusters, sheets, fillaments and voids can be defined with the number of axes above $\lambda$.
-Forero et. al. found in \cite{forero2009} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\
+Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to cluster in the respective eigenaxes, and viceversa. 
+With this characterization, clusters, sheets, fillaments and voids can be defined with the number of eigenvalues above $\lambda$.
+Forero et. al. found in \cite{forero2009} that the critical value that better reproduces the correct morphological populations was $\lambda = 0.2$. \\
 
@@
 
-% Example table
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
-
 \section{Conclusions}

### 2017-10-28 Paper/paper.tex
solved problem with bibtex compilation

@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
+\title[No Title]{No Title}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[K. T. Smith et al.]{
-Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
-\\
+\author[No Author et al.]{
+No Authors$^{1}$\thanks{E-mail: }\\
+%A. N. Other,$^{2}$
+%Third Author$^{2,3}$
+%and Fourth Author$^{3}$
 % List of institutions
-$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{1}$No affiliation\\
 }
@@
 With this characterization, clusters, sheets, fillaments and voids can be defined with the number of eigenvalues above $\lambda$.
-Forero et. al. found in \cite{forero2009} that the critical value that better reproduces the correct morphological populations was $\lambda = 0.2$. \\
+Forero et. al. found in \cite{Forero2009} that the critical value that better reproduces the correct morphological populations was $\lambda = 0.2$. \\
 

### 2017-10-28 Paper/paper.tex
minor edits

@@
-% mnras_template.tex
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
 \documentclass[a4paper,fleqn,usenatbib]{mnras}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
@@
 
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
 \usepackage{graphicx}	% Including figure files
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+No abstract.
 \end{abstract}
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+\section{The Illustris-1 Simulation}
+Illustris-1 is a highly resolved cosmological simulation. 
+It reproduces large-scale statistical features of the Universe, such
+as the galaxy population of massive clusters, as well as small-scale
+properties such as the morphology of galaxies and detailed values for
+their stellar and gas content.
 
-\cite{Forero2009}.
-
-\section{Illustris Simulation}
-Illustris-1, also known as Illustris, is a highly resolved
-cosmological simulation. It reproduces large-scale statistical
-features of the Universe, such as the galaxy population of massive
-clusters, as well as small-scale properties such as the morphology of
-galaxies and detailed values for their stellar and gas content.\\
-
-This was achieved by following the evolution of $2 \times 1820^3$ elements with dark mass resolution of $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$ and initial baryonic mass resolution of $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration in a periodic box of $106.5\text{Mpc}$.
-The $\Lambda \text{CDM}$ cosmology of this run follows: $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
+The Illustris-1 simulation followed  the evolution of $2 \times 1820^3$
+elements with dark mass resolution of $m_{\text{DM}} = 6.26\cdot
+10^6\text{M}_{\odot}$ and initial baryonic mass resolution of
+$\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a
+glass-like configuration in a periodic box of $106.5\text{Mpc}$. The
+$\Lambda \text{CDM}$ cosmology of this run follows:
+$\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$,
+$\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$,
+$\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms} 
 ^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy
@@
 
-The evolution in time was performed with the hydrodynamic code AREPO
+This work was  performed using the hydrodynamic code AREPO
 \cite{Arepo}, which combines a moving Voronoi tessellation with the
@@
 \subsection{ Characterizing Mass Functions}
-A mass function is the number density $n(M)$ of objects of determined mass $M$.
-Due to the large range of orders of magnitud in which these quantities span, the mass function is often represented in logarithmic scales on both sides. 
-The discretization of these mass functions is simply the histogram of the logarithmic masses of the studied group of objects. 
-In Illustris, as in all simulations, we have clear determination of volumes.
-This volume is constant over all the sample of galaxies studied and is to be taken the constant volume of the simulation $V = \left(106.5\text{Mpc}\right)^3$.
-In this sense, the relation expressed by a mass function is
 
+To characterize specific properties of these mass functions, we use
+the Press-Schechter function
 \begin{equation}
-n(M)Vd\log{(M)} =  dN
-\end{equation}
-
-To characterize specific properties of these mass functions, we use the Press-Schechter function \ref{eq:Schechter}. 
-It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
-Although its ansatz has been demonstrated to be inaccurate for our observable universe \cite{inaccurateSchechter}, the final expression is very well fitted to the mass functions of the local universe \cite{wellfitSchechter}.\\
-
-\begin{equation}
-n\left( M \right) = n_*\left( \frac{M}{M_*} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_*}\right)}
+n(M) = n_\star\left( \frac{M}{M_\star} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_\star}\right)},
 \label{eq:Schechter}
 \end{equation}
-
-The Schechter function \ref{eq:Schechter} is fully defined by the three parameters $(n_*,M_*,\alpha)$. 
-The number density factor $n_*$ is just a normalization factor which varies depending on the studied system. 
-The mass scale factor $M_*$ may be interpreted as the mass that separates the power-law regimen $M \ll M_*$ and the exponential regimen $M \gg M_*$. 
-This transition graphically resemnles a knee, which is the reason why $M_*$ is referred as the knee-mass.
+%
+where $n$ is the number of galaxies per unit volume per dex in mass.
+This function is fully described by the three parameters: $n_\star$,
+$M_\star$ and $\alpha$; $n_\star$ is a normalization factor, the mass
+scale factor $M_\star$ is that separates the power-law regimen at $M
+\ll M_*$ and the exponential regimen for $M \gg M_*$. 
+This transition graphically resembles a knee, which is the reason why
+we refer in this paper $M_*$ as the knee-mass.
 The faint-end slope $\alpha$ is directly related to the exponent of the power-law at the low-mass regime.
 In logarithmic scales, it is clearly interpreted as the slope of the low-mass regime.\\
+
+and the scalars $n_{\star}$, $M_{\star}$ and $\alpha$ are 
+$M$.
+
+It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
+Although its ansatz has been demonstrated to be inaccurate for our
+observable universe \cite{inaccurateSchechter}, the final expression
+is very well fitted to the mass functions of the local universe
+\cite{wellfitSchechter}.\\
 

### 2017-10-28 Paper/paper.tex
edits

@@
 
+The first objective of this paper is to compare Illustris-1 against 
+the observational results obtained by \cite{Jones2016}.
+In that work the authors study a gas rich sample built with the
+ALFALFA survey to define the effects of different environments on the
+gas mass function.
+The second goal is to extend this environmental classification to 
+the stellar and black hole mass functions. 
+Finally, we study these environmental trends in the baryonica galaxy
+properties in terms of dark matter halo mass segregation and the dark
+matter cosmic web.
+
 \section{The Illustris-1 Simulation}
@@
 
-\subsection{ Characterizing Mass Functions}
+\subsection{Characterizing Mass Functions}
 
-To characterize specific properties of these mass functions, we use
-the Press-Schechter function
+To characterize the mass functions in Illustris data we use
+the Press-Schechter expression
 \begin{equation}
@@
 $M_\star$ and $\alpha$; $n_\star$ is a normalization factor, the mass
-scale factor $M_\star$ is that separates the power-law regimen at $M
-\ll M_*$ and the exponential regimen for $M \gg M_*$. 
+scale factor $M_\star$ is that separates the power-law regimen at
+$M\ll M_*$ and the exponential regimen for $M \gg M_*$. 
 This transition graphically resembles a knee, which is the reason why
 we refer in this paper $M_*$ as the knee-mass.
-The faint-end slope $\alpha$ is directly related to the exponent of the power-law at the low-mass regime.
-In logarithmic scales, it is clearly interpreted as the slope of the low-mass regime.\\
+The faint-end slope $\alpha$ is directly related to the exponent of
+the power-law at the low-mass regime.
 
-and the scalars $n_{\star}$, $M_{\star}$ and $\alpha$ are 
-$M$.
+This expression comes from a formalism describing the hierarchical
+formation of gravitationally bound structures in an expanding
+Friedmann universe arriving to a self-similar state of "equilibrium"
+for its mass function \cite{Schechter1976}. 
+Although its ansatz is not correct \cite{inaccurateSchechter}, the
+final expression in Eq. (\ref{eq:Schechter}) provides a good
+description of galaxy mass and luminostiy functions
+\cite{wellfitSchechter}.
 
-It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
-Although its ansatz has been demonstrated to be inaccurate for our
-observable universe \cite{inaccurateSchechter}, the final expression
-is very well fitted to the mass functions of the local universe
-\cite{wellfitSchechter}.\\
+We also impose a magnitude cut in the $r$ band of $M_r<-19$ to keep
+a galaxy sample that resembles the one used in previous observational
+studies. 
+To obtain the Schechter parameters that characterize each numerical
+mass function, we used MCMC to obtain the fit with best likelihood.
 
-To obtain the Schechter parameters that characterize each numerical mass function, we used MCMC to obtain the fit with best likelihood. 
-With this, we could also ...\\
+\subsection{Resolution Effects}
 
-As Illustris is a cosmological simulation, it is subject to resolution and numerical biases.
-The most important bias in this study is related to the minimum mass of discrete elements in the simulation.
-Each mass considered here is subject directly or indirectly this resolution restriction, and the effect it causes is specially evident in the produced mass functions. 
-We used Illustris-2,3, which are less resoluted copies of Illustris-1, to show this effect on the mass functions \ref{fig:resolution effects}. 
-Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study.
-This mass cut has no apparent systematical way to be calculated and therefore, we choose it having into account the performance of the respective Schechter fit.\\
+As every simulation, Illustris is subject to limitations due to its
+numerical finite resolution.
+The most important limitation in this study is related to its
+resolution as it puts a constraint on the minimum mass that can be 
+confidently resolved.
+We use Illustris-2, and Illustris-3, lower resolution versions of
+Illustris-1 to quantify this effect.
+
+Figure \ref{fig:resolution_effects} shows the cumulative gas mass
+function for the three simulations after making the magnitude cut
+$M_r<-19$.
 
@@
 	\includegraphics[width=\columnwidth]{./pics/MassResolution.png}
-    \caption{The effect on mass resolution on mass functions of Illustris-1,2,3. (Masses have units $10^{10}M_\odot$)} 
-    \label{fig:resolution effects}
+    \caption{Gas mass functions in the simulations Illustris-1,2,3. (Masses have units $10^{10}M_\odot$)}  
+    \label{fig:resolution_effects}
 \end{figure}
 
-\subsection{Defining the environment}
+\subsection{Environment definitions}
 
-Given the current interest in the study of the dependence of observational HIMFs on the environment and the wide difference of the conclusions of these studies, the main scope of this work is to verify if the any results obtained observationally are supported by a similar analysis in the cosmological simulation Illustris.\\
+In this paper we extend that 
+study observationally-comparable, we follow the 3rd nearest neighbor
+(3NN) definition of environment proposed by Jones et
+al.
+
+obtained observationally are supported by a similar analysis in the
+cosmological simulation Illustris.\\
 
 For this purpose, we take two approaches to analyze the dependence of mass functions on environment. 
-On one hand, to make our study observationally-comparable, we follow the 3rd nearest neighbor (3NN) definition of environment proposed by Jones et al. \cite{Jones2016}. 
-On the other hand, to confirm our results, we use a computational and theoretical definition of environment (T-Web) of completely different nature proposed by Forero et al. \cite{Forero2009}.
+On one hand, to On the other hand, to confirm our results, we use a computational and theoretical definition of environment (T-Web) of completely different nature proposed by Forero et al.
+\cite{Forero2009}.
 

### 2017-10-28 Paper/paper.tex
cut long lines

@@
 \begin{equation}
-n(M) = n_\star\left( \frac{M}{M_\star} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_\star}\right)},
+n(M) = n_\star\left( \frac{M}{M_\star} \right)^{-\alpha+1}\exp \left( -\frac{M}{M_\star}\right),
 \label{eq:Schechter}
@@
 
-Jones et al. \cite{Jones2016} the SDSS \cite{SDSS2011} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
-This SDSS catalogue was chosen to be optically-selected and volume-limited to account for apparent lonely galaxies in ALFALFA with increasinf distance. 
-For this reason, they pre-selected galaxies brighter than $M_r = -18.9$ in this survey.\\
+Jones et al. \cite{Jones2016} the SDSS \cite{SDSS2011} catalogue to
+define the environment of galaxies in the ALFALFA \cite{ALFALFA}
+survey. 
+This SDSS catalogue was chosen to be optically-selected and
+volume-limited to account for apparent lonely galaxies in ALFALFA with
+increasinf distance.  
+For this reason, they pre-selected galaxies brighter than $M_r =
+-18.9$ in this survey.
 
-To quantify the environment , for each reference galaxy in ALFALFA, they calculated the projected distance in the sky to the third nearest neighbor belonging to the pre-selected SDSS catalogue.
+To quantify the environment , for each reference galaxy in ALFALFA,
+they calculated the projected distance in the sky to the third nearest
+neighbor belonging to the pre-selected SDSS catalogue. 
 This projected distance in the sky defines a numeric-surface density for each reference galaxy.
-To do so, first, they filtrated candidate neighbors by their radial velocity relative to the reference galaxy which had to be within $450km/s$.
-According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the use of projected distances. \\
+To do so, first, they filtrated candidate neighbors by their radial
+velocity relative to the reference galaxy which had to be within
+$450km/s$. 
+According to Hubble's law, this effectively restricts the candidate
+galaxies to a smaller radial range, reducing apparent closer galaxies
+arising from the use of projected distances.
 
@@
 For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained. 
-%The analysis was specifically performed over the Schechter parameters of the Knee-mass $M^*$ and the faint-end slope $\alpha$. \\
+%The analysis was specifically performed over the Schechter parameters
+%of the Knee-mass $M^*$ and the faint-end slope $\alpha$. \\
 
-As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{Jones2016}, we use the same specifications to calculate the environment.
+As we want to replicate as closely as possible the method effectuated
+by Jones et. al \cite{Jones2016}, we use the same specifications to
+calculate the environment. 
 We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
-We do not perform the study directly on HIMFs because this would require some extense calculations. We take the gas mass function as a first approximation.\\
+We do not perform the study directly on HIMFs because this would
+require some extense calculations. We take the gas mass function as a
+first approximation.
 
 \subsubsection{The cosmic web method}
-To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature. 
+To complement and verify the analysis performed with the third nearest
+neighbor method, we chose a complementary method of completely
+different nature.  
 The chosen method was developed by Forero et al. \cite{Forero2009}. 
-It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the smoothened DM density field to classify galaxies into four morphological environments.\\
+It uses the Hessian \ref{eq:hessian} of the gravitational potential
+obtained from the smoothened DM density field to classify galaxies
+into four morphological environments.
 
@@
 
-Specifically, we diagonalize the Hessian matrix of the gravitational potential $\phi$ obtaining three eigenvalues. 
-This matrix encodes the local curvature of the gravitational potential. 
-Specifically, these eigenvalues determine the concavity of $\phi$ on the principal axes, at each point. 
-We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$. 
-Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to cluster in the respective eigenaxes, and viceversa. 
-With this characterization, clusters, sheets, fillaments and voids can be defined with the number of eigenvalues above $\lambda$.
-Forero et. al. found in \cite{Forero2009} that the critical value that better reproduces the correct morphological populations was $\lambda = 0.2$. \\
+Specifically, we diagonalize the Hessian matrix of the gravitational
+potential $\phi$ obtaining three eigenvalues.  
+This matrix encodes the local curvature of the gravitational
+potential.  
+Specifically, these eigenvalues determine the concavity of $\phi$ on
+the principal axes, at each point.  
+We use these eigenvalues to interpret the tendence of mass to cluster
+with reference with some given threshold $\lambda$.  
+Eigenvalues bigger than $\lambda$ are interpreted as a local tendence
+of mass to cluster in the respective eigenaxes, and viceversa.  
+With this characterization, clusters, sheets, fillaments and voids can
+be defined with the number of eigenvalues above $\lambda$. 
+Forero et. al. found in \cite{Forero2009} that the critical value that
+better reproduces the correct morphological populations was $\lambda =
+0.2$.
 
-With these specifications, we could obtain mass functions for galaxies belonging to clusters, fillaments and sheets.
-The amount of galaxies belonging to voids was strongly affected by the mentioned mass cuts and could not produce reasonable mass functions to analyze.
+With these specifications, we could obtain mass functions for galaxies
+belonging to clusters, fillaments and sheets. The amount of galaxies
+belonging to voids was strongly affected by the mentioned mass cuts
+and could not produce reasonable mass functions to analyze.
 
@@
 
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-28 Paper/paper.tex
nuevo orden de las graficas
minor edits in caption

@@
 
-Figure \ref{fig:resolution_effects} shows the cumulative gas mass
-function for the three simulations after making the magnitude cut
-$M_r<-19$.
-
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/MassResolution.png}
-    \caption{Gas mass functions in the simulations Illustris-1,2,3. (Masses have units $10^{10}M_\odot$)}  
-    \label{fig:resolution_effects}
-\end{figure}
-
 \subsection{Environment definitions}
@@
 \begin{equation}
-E =  mc^2
+H
 \label{eq:hessian}
@@
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
 	\includegraphics[width=\columnwidth]{./pics/F19_quartilesGas.png}
-    \caption{\textbf{Upper side}: Schechter fits of each gas mass
+    \caption{\textbf{Upper panel}: Schechter fits of each gas mass
       function for each environmental quartile (tendence) using the 3rd nearest
-      neighbor definition.\textbf{Down side}: Knee-mass $m_\ast$ and
+      neighbor definition.\textbf{Lower panel}: Knee-mass $m_\ast$ and
       the faint end slope $\alpha$ values obtained from the Schechter
@@
 
+% Quartiles Stellar
+\begin{figure}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesSellar.png}
+    \caption{Similar to figure \ref{fig:quartilesGas} using stellar mass} 
+    \label{fig:quartilesStellar}
+\end{figure}
+
+% Quartiles BH
+\begin{figure}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesBH.png}
+    \caption{Similar to figure \ref{fig:quartilesGas} using BHs mass.} 
+    \label{fig:quartilesBH}
+\end{figure}
+
+% Quartiles DM
+\begin{figure}
+	\includegraphics[width=\columnwidth]{./pics/F19_quartilesDM.png}
+    \caption{Similar to figure \ref{fig:quartilesGas} using DM.} 
+    \label{fig:quartilesDM}
+\end{figure}
+
 % Tweb gas
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
 	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_Gas.png}
-    \caption{\textbf{Upper side}: Schechter fits of each gas mass
+    \caption{\textbf{Upper panel}: Schechter fits of each gas mass
       function for each morphological environment characterized by the
-      T-Web algorithm proposed by Forero et al.\textbf{Down side}:
+      T-Web algorithm proposed by Forero et al.\textbf{Lower panel}:
       Knee-mass $m_\ast$ and the faint end slope $\alpha$ values
@@
 
-% Quartiles DM
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/F19_quartilesDM.png}
-    \caption{Similar to figure \ref{fig:quartilesGas} using DM.} 
-    \label{fig:quartilesDM}
-\end{figure}
-
-% Tweb DM
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_DM.png}
-    \caption{Similar to figure \ref{fig:TwebGas} using DM.} 
-    \label{fig:TwebDM}
-\end{figure}
-
-% Quartiles Stellar
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/F19_quartilesSellar.png}
-    \caption{Similar to figure \ref{fig:quartilesGas} using stellar mass} 
-    \label{fig:quartilesStellar}
-\end{figure}
-
 % Tweb Stellar
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
 	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_Stellar.png}
@@
 
-% Quartiles BH
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{./pics/F19_quartilesBH.png}
-    \caption{Similar to figure \ref{fig:quartilesGas} using BHs mass.} 
-    \label{fig:quartilesBH}
-\end{figure}
-
 % Tweb BH
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
 	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_BH.png}
@@
     \label{fig:TwebBH}
+\end{figure}
+
+% Tweb DM
+\begin{figure}
+	\includegraphics[width=\columnwidth]{./pics/F19_T-Web_DM.png}
+    \caption{Similar to figure \ref{fig:TwebGas} using DM.} 
+    \label{fig:TwebDM}
 \end{figure}
